---
title: "ACST886 Assignment Question3"
author: "Chang Liu"
date: "22/08/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 3

### Part a
Present Value:
$PV=\sum^{30}_{t= 1} Commision\times ({\frac{1}{1+i}})^t $
```{r}
Commision<-1000
L<-600000
int<-.035
PV<-sum(Commision*(1/(1+int))^(1:30))
PV
```
### Part b

The interest that the bank requires on its fund should be less than 3.5%, thus the aount paid by Bill actually includes the commission paid to Broker.

### Part c
The total amount paid by Bill
```{r}
Tol<-PV+L
Tol
```
The effective interest rate
$Tol=\sum^{30}_{t= 1} (Commision+Instalment)\times ({\frac{1}{1+i_e}})^t $
According to the formula above, in order to get the effective interest required, we need to get the root of equation:
$Tol-\sum^{30}_{t= 1} Commision\times ({\frac{1}{1+i_e}})^t=0 $
Using uniroot function, the answer is obtained by following steps.
```{r}
instal<-32622.8
g<-function(i){Tol-sum(instal*(1/(1+i))^(1:30))}
root2<-uniroot(g,c(0,1),tol = 0.0001)
i=root2$root
i
```
### Part d
Bill's annual payments consist 2 parts: installment to pay back $600000 mortgage and 1000 to pay the commision.
First the new instalment should be determined using the formula:
$L=\sum^{30}_{t= 1} instal2\times ({\frac{1}{1+i_e}})^t $
```{r}
h<-function(instal2){L-sum(instal2*(1/(1+i))^(1:30))}
root3<-uniroot(h,c(0,600000),tol = 0.01)
instal2=root3$root
cat("Annul_payment:",instal2)
```
Finally we can calculate the difference between 2 annual payments:
```{r}
diff<-instal-instal2
diff
```

That is the payment is increased by 969.0094